Investigating Determinism of Game Engines for Autonomous Vehicle Verification

### 2020-05-15 paper/cav_determinisim_main.tex
Replied to todo questions.

The tests are listed in Table~\ref{TableOfExperiments} and were chosen to cover a range of interactions between actor types. 
%
Tests 1 \& 2 involve 2 vehicles meeting at a junction where they do not collide (test 1) and when they do tiggering a \textit{event hit} callback in the game engine (test 2). In both cases the trajectories of the vehicles are hard-coded to follow a set of waypoints spaced at $0.1$m \todo[inline]{AG: is this value correct or should it be 2.0m?} intervals using a PID controller. In test 3 a mixture of different actor types are introduced where two vehicles drive without collision and a pedestrian walks across the road at a crossing point. In test 4 this pedestrian collides with one of the vehicles at the crossing, triggering a \textit{event hit} callback, see Fig~\ref{Test_a}. Similar to vehicles, pedestrians navigate via a set of regularly spaced waypoints at $0.1$m intervals using the A* algorithm which is the default controller for the Carla pedestrian actors. Tests 5 \& 6 involve only pedestrians that do not collide (test 5) and that do collide (test 6), see Fig.~\ref{Test_b}.

>>>>

The tests are listed in Table~\ref{TableOfExperiments} and were chosen to cover a range of interactions between actor types. 
%
Tests 1 \& 2 involve 2 vehicles meeting at a junction where they do not collide (test 1) and when they do tiggering a \textit{event hit} callback in the game engine (test 2). In both cases the trajectories of the vehicles are hard-coded to follow a set of waypoints spaced at $0.1$m \todo[inline]{AG: is this value correct or should it be 2.0m? AG-reply: The granularity of the trajectory waypoints is 0.1m, but the lookahead distance that the actors use is 2m ... actors would ignore trajectory waypoints that are less than 2.0m away from them.} intervals using a PID controller. In test 3 a mixture of different actor types are introduced where two vehicles drive without collision and a pedestrian walks across the road at a crossing point. In test 4 this pedestrian collides with one of the vehicles at the crossing, triggering a \textit{event hit} callback, see Fig~\ref{Test_a}. Similar to vehicles, pedestrians navigate via a set of regularly spaced waypoints at $0.1$m intervals using the A* algorithm which is the default controller for the Carla pedestrian actors. Tests 5 \& 6 involve only pedestrians that do not collide (test 5) and that do collide (test 6), see Fig.~\ref{Test_b}.
